---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}
unzip("activity.zip")
data <- read.csv("activity.csv", header=T, sep=",")
data$date <- as.Date(data$date)

library(knitr)
opts_chunk$set(fig.path="figure/")
```


## What is mean total number of steps taken per day?

First let's look at the steps per date data through an histogram.
```{r}
steps.per.date <- with(data, tapply(steps, date, sum, na.rm=T))
hist(
  steps.per.date,
  xlab="Steps per Date", ylab="Count",
  main="Steps per Date Histogram",
  col="blue"
)
```

As per the mean and median, we have the following:
```{r}
mean(steps.per.date)
median(steps.per.date)
```

## What is the average daily activity pattern?

First, we need to calculate the averages for each of the 5-min intervals. Then we'll plot it in a time-series plot.
```{r}
intervals <- unique(data$interval)
avg.per.interval <- with(data, tapply(steps, interval, mean, na.rm=T))

plot(
  intervals,
  avg.per.interval,
  xlab="5-minute Interval", ylab="Average",
  main="Average Across all Days for each Interval",
  col="darkgreen", type="l"
)
```

As per the 5-min interval with the highest average of steps, we apply the `max` function to it:
```{r}
index <- which.max(avg.per.interval)
names(index)
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
